A molecular taxonomy of tumors independent of tissue-of-origin

### 2021-07-02 text/survival.Rmd

>>>>

To compare our pathway-based clustering to other published methods, we evaluated
the performance in predicting time to death (tdeath) with other published
classification models. We downloaded cluster membership from two studies
conducted within the TCGA consortium [@hoadleyMultiplatformAnalysis2014;
@hoadleyCellofOriginPatternsDominate2018].  We generated tdeath predictions from
uniform random p, by inverting the cumulative distribution function of our death
probability function. Using the actual tdeath from TCGA as the reference, we
show that our pathway-based clustering (referred to as kNN) had slightly better
performance compared to COCA [@hoadleyMultiplatformAnalysis2014], iCluster
[@hoadleyCellofOriginPatternsDominate2018] and tissue-of-origin (tis). (**S5A
Fig**). Additionally, we computed the entropy of the error distribution in
predictions (**S5B Fig**).  All models had similar performance with kNN
performing slightly better as indicated by a slightly smaller error entropy.
